Trends of SDR in Thessaloniki

### 2023-09-18 Article.Rmd
Commit 2023-09-18 14:14

## order columns
LT <- LT[,c(
      "Sky condition",
      "Season",
      "Trend [%/year]"
      )]

@@

## arrange columns
spp <- spp[,c(
      "Sky condition",
      "Season",
      "Trend [%/year]", 
      "Trend p-value", 
      "Statistical signif. [%]"
      )]

>>>>

## order columns
LT <- LT[,c(
      "Sky condition",
      "Trend [%/year]",
      "Trend p-value"
      )]

@@

## arrange columns
spp <- spp[,c(
      "Sky condition",
      "Season",
      "Trend [%/year]", 
      # "Trend p-value", 
      "Statistical signif. [%]"
      )]
